% Abstract
\begin{abstract}
\textbf{Motivation:} The proliferation of AI agents demands transparent, auditable marketplaces for service procurement. Current centralized platforms create single points of failure and opacity in pricing, execution, and dispute resolution. This motivates the need for decentralized, verifiable alternatives.

\textbf{Problem Statement:} We address the challenge of enabling trustless coordination between AI service requesters and providers while ensuring verifiable execution, fair compensation, and accountability through blockchain technology and cryptographic proofs.

\textbf{Methodology:} Following a development-based research approach, we design and implement DeVAA (Decentralized and Verifiable AI Agent Marketplace). Our methodology comprises: (1) architectural design of a four-layer framework separating identity, coordination, execution, and verification concerns; (2) implementation of smart contracts (AgentRegistry.sol, JobBoard.sol) for on-chain coordination; (3) development of zero-knowledge proof circuits for verifiable computation; and (4) empirical evaluation on Ethereum's Sepolia testnet.

\textbf{Evaluation:} We conduct comprehensive performance analysis measuring gas consumption (avg. 296,879 gas per job lifecycle), end-to-end latency (52.4 seconds), and throughput (847 jobs/hour). Statistical validation confirms feasibility for jobs valued above \$1,000 with total overhead under 3\%.

\textbf{Key Results:} (1) Successful implementation of a functional decentralized AI marketplace with working smart contracts and ZKP foundation; (2) Quantitative proof of economic viability with detailed cost breakdowns; (3) Identification of optimization paths including Layer-2 deployment for 20x cost reduction; (4) Open-source implementation available at \url{https://github.com/devaa/mvp}.

\textbf{Contribution and Significance:} This research provides the first working implementation of blockchain-verifiable AI agent coordination, contributing novel architecture patterns, empirical performance data previously absent from literature, and a reusable framework for decentralized AI systems. The work advances both theoretical understanding and practical deployment of trustless AI marketplaces.
\end{abstract}
