\chapter{Appendix C: Completed Ethics Application Form}
\label{appendix:ethics}

\section*{Section 1: Project Details}
\begin{longtable}{p{0.4\textwidth}p{0.55\textwidth}}
Project title & DeVAA: A Decentralized and Verifiable AI Agent Marketplace \\
Student name & Youssef Amjahdi, Abdelmounaim Sadir \\
Student Number & GH1026457 (Youssef), GH1026144 (Abdelmounaim) \\
Supervisor & Dr. Loui Al Sardy \\
Course category & Masters (ticked) \\
Course/module title & MSc Data Science, AI, and Digital Business \\
Intended research start/end dates & April 2025 -- September 2025 \\
Country fieldwork will be conducted in & Germany (No actual fieldwork; development is remote) \\
\end{longtable}

\section*{Section 2: Research methods summary}
\begin{itemize}
  \item Literature Review (ticked)
  \item Other (ticked): Proof-of-Concept (PoC) System Development and Performance Benchmarking
\end{itemize}
\textbf{Overview of the project (\~150 words).} This research designs, builds, and evaluates a novel software framework for a decentralized and verifiable AI agent marketplace. The methodology begins with a comprehensive literature review to identify the research gap across decentralized systems, verifiable computation, and AI agent markets. We then execute a design science process to specify the architecture and implement a functional minimum viable product (MVP) including smart contracts, an off-chain agent runner, and a verification workflow. Data collection is limited to benchmarking the performance of the software itself (e.g., transaction costs, processing time, and end-to-end latency) to assess technical feasibility and trade-offs. No human data are collected at any stage, and no direct interaction with human participants occurs. The study focuses on technical evaluation of the implemented system under controlled conditions, emphasizing reproducibility and transparency.

\section*{Section 3: Research Participants}
Will your research involve human participants? \textbf{No (ticked).} \\
As no human participants will be recruited or observed, all subsequent items in Section 3 are \textbf{Not Applicable (N/A)}.

\section*{Section 4: Secondary data analysis}
Are the data in the public domain? \textbf{Yes (ticked).} \\
Explanation: The secondary data used in this thesis consists exclusively of publicly available academic papers and scholarly articles for the literature review. No private or restricted datasets are used.

\section*{Section 5: Data storage and security}
GDPR Compliance: \textbf{Yes (ticked).} \\
No personal data from human participants will be collected, stored, or processed. The only data generated are (i) the project's source code, stored during development in a private GitHub repository with access control, and (ii) anonymized performance metrics (e.g., timings and transaction fees) produced by the software. No special-category personal data are processed. Research artifacts will be retained for reproducibility and archived securely according to institutional policies.

\section*{Section 6: Ethical Issues}
While this research does not involve direct ethical issues concerning human participants, the subject matter has significant future ethical implications. Real-world deployments of decentralized AI agent marketplaces raise concerns around algorithmic bias in AI agents, potential economic displacement via automation, misuse for malicious activities (e.g., collusion or exploitation), and data privacy risks if the framework were extended to handle sensitive user data. Our work confines itself to a technical proof-of-concept but provides a foundation that can inform future ethical guidelines, including transparency requirements, auditing mechanisms, and safeguards against abuse.

\section*{Section 8: Attachments}
\begin{itemize}
  \item The proposal for the project: \textbf{Yes (ticked).} Chapter~1 of this thesis serves as the proposal.
  \item All other items: \textbf{N/A (ticked).}
\end{itemize}

\section*{Section 10: Declaration}
Names: \textbf{Youssef Amjahdi, Abdelmounaim Sadir}. \\
Date: \textbf{\today}.

\section*{Study Information and Statement of Informed Consent}
\textbf{Not Applicable (N/A).} As this research does not involve human participants, a consent form is not required or used. The remainder of the standard consent template is intentionally left blank.
